---
title: "Demo of knitr chunk options"
output: 
  html_document:
    theme: flatly
    code_download: true
    code_folding: hide
---


```{r setup, include=FALSE, purl=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r libraries, class.source = "fold-show"}
# load libraries
library(tidyverse)
library(palmerpenguins)
```

- use `class.source = "fold-show"` to override global option `code_folding: hide` so the above chunk shows code by default

# Penguin bill dimensions

```{r penguins-plot, fig.path="my_figs/", dev=c("png","pdf"), dev.args=list(family='Palatino'), fig.cap = "My amazing penguins plot"}
penguins %>%
  ggplot(aes(
    x = bill_length_mm,
    y = bill_depth_mm,
    group = species
  )
  ) +
  geom_point(aes(
    color = species,
    shape = species
  ),
  size = 3,
  alpha = 0.8
  ) +
  geom_smooth(method = "lm", se = FALSE, aes(color = species)) +
  theme_minimal() +
  scale_color_manual(values = c("darkorange", "purple", "cyan4")) +
  labs(
    title = "Penguin bill dimensions",
    subtitle = "Bill length and depth for Adelie, Chinstrap and Gentoo Penguins at Palmer Station LTER",
    x = "Bill length (mm)",
    y = "Bill depth (mm)",
    color = "Penguin species",
    shape = "Penguin species"
  ) +
  theme(
    legend.position = c(0.85, 0.15),
    legend.background = element_rect(fill = "white", color = NA),
    plot.title.position = "plot",
    plot.caption = element_text(hjust = 0, face = "italic"),
    plot.caption.position = "plot"
  )
```

- use `fig.path` to specify where to save output
- use `dev=c("png","pdf")` to save an both .png and .pdf
- use `dev.args=list(family='Palatino')` to change font in .pdf output
- use `fig.cap` to automatically add a figure caption

# Child documents

- The `child ` option takes a character vector of paths to the child document(s)

```{r child="child_docs/another_plot.Rmd", fig.cap="Another plot"}
```


# Extracting R code

You can extract only R code with `knitr::purl("chunk_opts_demo.Rmd")`, which will save a corresponding .R script.

- Use `documentation = 2` to retain text as well
- Set `purl=FALSE` for any chunk you don’t want to extract
- You can turn a .R script into a .Rmd with `knitr::spin()`

# Resources 

- [Github repo](https://github.com/yihui/knitr-examples) with tons of knitr examples
- [Yihui's documentation](https://yihui.org/knitr/options/) on knitr chunk options
- [Chapter 11](https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html) of R Markdown Cookbook
