---
title: "Demo of divs in R Markdown"
output: 
  html_document: 
    css: css/custom.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r libraries, echo = FALSE}
library(tidyverse)
```

## Multi-column layouts with Pandoc's fenced divs

- create an "outside" `<div>` container with `::::`
- add inline CSS attribute `display: flex;`
- create "inside" `<div>` containers with `:::`

:::: {style="display: flex;"}

::: {}
Here is a plot with black points

```{r echo=FALSE}
mpg %>% 
  ggplot(aes(displ, hwy)) + 
  geom_point()
```
:::

::: {}
Here is a plot with blue points.

```{r echo=FALSE}
mpg %>% 
  ggplot(aes(displ, hwy)) + 
  geom_point(color = "blue")
```
:::

::::

## Note boxes aka "div tips"

- Create a .css file (e.g. `/css/custom.css`) with the styling info
- Save an icon image (will be referenced in your .css code)
- Use the `:::` syntax, which is converted to `<div>` tags by Pandoc

:::lightbulb
Here is a beautiful note box. You can customize this to look however you want. Credit: [Desirée de Leon](https://desiree.rbind.io/)
:::

## Include collapsable session info

- use `<details>` and `<summary>` tags for output folding

<details><summary>Session Info</summary>
```{r echo=FALSE}
sessioninfo::session_info()
```
</details>

# Resources 

- [Section 5.8](https://bookdown.org/yihui/rmarkdown-cookbook/multi-column.html) of R Markdown Cookbook on multi-column layouts

- [Blog post](https://desiree.rbind.io/post/2019/making-tip-boxes-with-bookdown-and-rmarkdown/) on creating custom div tips by Desirée de Leon

- [Section 7.12](https://bookdown.org/yihui/rmarkdown-cookbook/details-tag.html) of R Markdown Cookbook on the `<details>` disclosure element

- [A complete guide to Flexbox](https://css-tricks.com/snippets/css/a-guide-to-flexbox/)